Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-11 GHI_enh_04_investigate.tex
Commit 2024-09-10 12:14
Commit 2024-09-10 22:14
Commit 2024-09-11 09:08

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-10}

@@

\caption{ - empty caption - }\label{fig:P-energy-complete-3}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-4}

@@

\caption{ - empty caption - }\label{fig:P-energy-complete-4}
\end{figure}
\begin{figure}[H]

@@

\begin{verbatim}
2024-09-10 07:46:40.3 athan@sagan GHI_enh_04_investigate.R 1.579120 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-11}

@@

\caption{ - empty caption - }\label{fig:P-energy-complete-3}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-multi-1}

\caption{ - empty caption - }\label{fig:P-energy-complete-multi-1}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-multi-2}

@@

\caption{ - empty caption - }\label{fig:P-energy-complete-multi-2}
\end{figure}
\begin{figure}[H]

@@

\begin{verbatim}
2024-09-11 05:57:13.1 athan@sagan GHI_enh_04_investigate.R 1.539943 mins
\end{verbatim}

### 2024-09-11 article/article.tex
Commit 2024-09-11 09:08

\begin{figure}% [h!]
        {\centering
            \subfloat[\label{fig:P-energy-N}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-2} }\\
            \subfloat[\label{fig:P-energy-mean}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-3} }\\
            \subfloat[\label{fig:P-energy-sum}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-1} }
        }
    \caption{Time series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023. The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
\end{figure}

>>>>

\begin{figure}% [h!]
        {\centering
            \subfloat[\label{fig:P-energy-N}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-2} }\\
            \subfloat[\label{fig:P-energy-mean}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-3} }\\
            \subfloat[\label{fig:P-energy-sum}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-1} }
        }
    \caption{Time-series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023. The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
\end{figure}
